\documentclass[a4paper,12pt,oldfontcommands]{memoir}
\PassOptionsToPackage{hyphens}{url}
\usepackage{url}
\usepackage{hyperref}
\usepackage{doi}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\usepackage{wrapfig}
\usepackage{natbib}
\usepackage[acronym,nomain,toc=true]{glossaries}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\newtheorem{hypothesis}{Hypothesis}[chapter]

%
\OnehalfSpacing*
\OnehalfSpacing
%\usepackage{showframe}

\chapterstyle{ell}
%% Section Headings
\nouppercaseheads
\pagestyle{ruled}
% Section headings
\setsecheadstyle{\large\sf\raggedright}
\setsubsecheadstyle{\normalsize\sf\raggedright}
\setsubsubsecheadstyle{\normalsize\itshape\raggedright}
% Normal headings
\makeevenhead{ruled}{\sf\leftmark}{}{}
\makeoddhead{ruled}{}{}{\sf\rightmark}
\makeevenfoot{ruled}{\sf\thepage}{}{}
\makeoddfoot{ruled}{}{}{\sf\thepage}
% Chapter footer
\makeevenfoot{plain}{}{\sf\thepage}{}
\makeoddfoot{plain}{}{\sf\thepage}{}
% hopefully title page footers
\makeevenfoot{empty}{}{}{}
\makeoddfoot{empty}{}{}{}
% Title page instructions
\pretitle{\thispagestyle{empty}\begin{flushright}\LARGE\sffamily}
\posttitle{\par\end{flushright}}
\preauthor{\begin{flushright}\Large\sffamily}
\postauthor{\par\end{flushright}\vskip 0.5em}
\predate{\begin{flushright}\large\sffamily}
\postdate{\par\end{flushright}\thispagestyle{empty}}

\renewcommand{\partnamefont}{\huge\sffamily}
\renewcommand{\partnumfont}{\huge\sffamily}
\renewcommand{\parttitlefont}{\huge\sffamily}

%\setbeforesecskip{-1.5ex plus -.5ex minus -.2ex}
%\setaftersecskip{1.3ex plus .2ex}
%\setbeforesubsecskip{-1.25ex plus -.5ex minus -.2ex}
%\setaftersubsecskip{1ex plus .2ex}
%% End Section Headings
%\captionnamefont{\small}
%\captiontitlefont{\small}

\usepackage[labelfont=sf,font+=small]{caption}
\usepackage[labelfont=sf]{subcaption}

\usepackage{todonotes}

\renewcommand\bibname{Reference List}
\setsecnumdepth{subsection}
\settocdepth{subsection}

% llt: Define a global style for URLs, rather that the default one
\makeatletter \def\url@leostyle{%
\@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
\makeatother \urlstyle{leo}


% Table of contents styles
\renewcommand{\cftchapterpagefont}{\sffamily}
\renewcommand{\cftsectionpagefont}{\sffamily}
\renewcommand{\cftsubsectionpagefont}{\sffamily}

%\renewcommand*{\cftchapterfont}{\normalfont\scshape}
\renewcommand*{\cftchapterfont}{\bf\sffamily}

% \newcommand{\cftchapterfont}{\sffamily}
% \newcommand{\cftsectionfont}{\sffamily}

\renewcommand\cftbookpresnum{\sffamily}
\renewcommand\cftbookaftersnum{\sffamily}
\renewcommand\cftbookaftersnumb{\sffamily}

\renewcommand\cftpartpresnum{\sffamily}
\renewcommand\cftpartaftersnum{\sffamily}
\renewcommand\cftpartaftersnumb{\sffamily}


\renewcommand\cftchapterpresnum{\sffamily}
\renewcommand\cftchapteraftersnum{\sffamily}
\renewcommand\cftchapteraftersnumb{\sffamily}

\renewcommand\cftsectionpresnum{\sffamily}
\renewcommand\cftsectionaftersnum{\sffamily}
\renewcommand\cftsectionaftersnumb{\sffamily}

\renewcommand\cftsubsectionpresnum{\sffamily}
\renewcommand\cftsubsectionaftersnum{\sffamily}
\renewcommand\cftsubsectionaftersnumb{\sffamily}

% Acronym entry:
\newacronym{JIT}{JIT}{Just-In-Time}
\newacronym{HPC}{HPC}{High Performance Computing}
\makeglossaries

\newcommand{\refpageref}[1]{\ref{#1} (p.~\pageref{#1})}
\newcommand{\sectionpageref}[1]{Section~\ref{#1} (p.~\pageref{#1})}
\newcommand{\tablepageref}[1]{Table~\ref{#1} (p.~\pageref{#1})}
\newcommand{\figurepageref}[1]{Figure~\ref{#1} (p.~\pageref{#1})}
\newcommand{\citepos}[1]{\citeauthor{#1}'s \citeyearpar{#1}}
% For citing: Author et al.'s (2009) work on hustle and bustle...
%\newcommand{\gls}[1]{#1} % Fake Glossary command for pandoc

\title{Dynamic Load Balancing for Distributed, Interdependent Tasks}
\author{Peter Davis}
%\date{}                                           % Activate to display a given date or no date
\begin{document}
\frontmatter
\maketitle

\pagebreak
\tableofcontents
\vfill
\pagebreak
\printglossary[type=\acronymtype,title=Abbreviations]
\vfill
%\pagebreak
%\listoffigures
%\pagebreak
%\listoftables

\chapter{Abstract}\label{abstract}

Abstract goes here

\subsubsection{Keywords:} 
keywords, go, here.

\mainmatter
% Chapter 1

\chapter{Introduction} % Main chapter title

\label{Chapter1} % For referencing the chapter elsewhere, use \ref{Chapter1} 

%----------------------------------------------------------------------------------------

% Define some commands to keep the formatting separated from the content 
\newcommand{\keyword}[1]{\textbf{#1}}
\newcommand{\tabhead}[1]{\textbf{#1}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\file}[1]{\texttt{\bfseries#1}}
\newcommand{\option}[1]{\texttt{\itshape#1}}

\section{Introduction}
The proliferation of streaming data sources such as optical sensors, health tracking sensors, and social networks has increased greatly in the previous 10 years, and with it the the desire to has the desire to understand and analyse this streaming data. The increase in computing power has similarly allowed computing simulations to become increasingly useful as a method of predicting and understanding various processes occurring, whether they be physical, social or purely theoretical.

This thesis seeks to address the problem of having multiple, potentially interrelated, heterogenous computational tasks that are long running or streaming tasks. The problem is broken up into the following parts:

\begin{enumerate}
\item Load balancing heterogenous long-running jobs between heterogenous computing hardware
\item Providing an api for job dependency graph
\item Providing an inter-job communication api
\item Providing an intra-job communication api
\end{enumerate}

The system is built using Extempore, a high performance lisp environment. This system was originally built for use in real-time cyThe benefits of being built in Extempore include:

\begin{itemize}
\item Providing a direct access to system devices via its C interoperability
\item Extempore \gls{JIT} compiles all code via the LLVM compiler to x86 bitcode, providing high performance program execuition
\item Dynamic code redefinition, allowing extempore processes to be retargeted with new functionality as is required
\end{itemize}

\chapter{Literature Review}

\section{Load Balancing}



Sees load balancing as a task done once by a job router, does not include the idea of redistributing the jobs once they are scheduled.
\cite{1675365}

``A load balancing algorithm consists of three components.

1) The information policy specifies the amount of load
and job information made available to the job placement
decision maker(s), and the way by which the information
is distributed.
2) The transfer policy determines the eligibility of a
job for load balancing based on the job and the loads of
the hosts.
3) The placement policy decides, for eligible jobs, the
hosts to which the jobs should be transferred.''
\cite{6176}

\subsection{Dynamic vs Static}


\cite{alakeel2010guide}

Dynamic vs static definition
\cite{1702040}

\cite{Anshelevich:2002:SLB:509907.509968}

Queuing system M/M/n

\cite{121756}

\subsection{Centralised vs Decentralised}

``In a centralized load balancing system, the global load information is collected at a single node, called the central scheduler. The other nodes, called local nodes, send their load status messages to the central scheduler. All load balancing decisions are made at the central scheduler based on the collected messages.

In a decentralized load balancing system, each node broadcasts its load information periodically to the other nodes to update their locally maintained load tables. Every node performs its node selection action. This can be done by having every node keep track of the global system load status continually.
''
\cite{472412}

``The scalability of the centralized algorithms,
GLOBAL and CENTRAL, however, is also
very good, at least up to 49 hosts. In constrast, DISTED
scales quite badly. We can see two conflicting factors in
action. On the one hand, an increase in system size makes
it easier to find a lightly loaded host. On the other hand,
the message overhead per host grows linearly with system
size, The composite effect is a moderately rising curve for
the normalized response time.''
\cite{6176}


Centralised 
\cite{121756}


\subsection{Homogenous vs Heterogenous Jobs}



\subsection{Homogenous vs Heterogenous Hardware}

uses homogenous system
\cite{6176}


\subsection{Measuring Load}

Traditional \gls{HPC} tasks are typically CPU bound, requiring processing power to (for example) advance their simulations forward in time, whilst Big Data tasks are typically memory and storage bound.

Measuring multiple load sources
\cite{1039771}


\section{Dependency Graph}

\section{Communication Systems}

\subsection{Inter-Job}

Actor 

Channel

\subsection{Intra-Job}

MPI

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{System Description}

\section{Architecture}

\section{Master Controller}

\section{Job Controller}

\section{Worker}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{System Demonstration}

\chapter{Discussion}

\chapter{Conclusion}


% Uncomment to add bibliography
\bibliographystyle{unsrtnat}
\bibliography{references}

\appendix
\appendixpage

\chapter{Appendix}

\listoftodos

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
